A Massive Molecular Gas Reservoir in the $z$\,=\,2.221 Type-2 Quasar Host Galaxy SMM\,J0939+8315 lensed by the Radio Galaxy 3C220.3

### 2015-07-21 skeleton.tex
compare type-2 qso onwards

%\documentclass{emulateapj}
\documentclass[twocolumn,apj,numberedappendix]{emulateapj}
\usepackage{hyperref}
\newcommand{\vdag}{(v)^\dagger}
\newcommand{\myemail}{tleung@astro.cornell.edu}
\newcommand{\Msun}{\mbox{$M_{\odot}$}}
\newcommand{\Rsun}{\mbox{R$_{\odot}$}}
\newcommand{\Lsun}{\mbox{L$_{\odot}$}}
\newcommand{\rarr}{$\rightarrow$}
\newcommand{\CO}{\mbox{CO($J$\,=\,3\,$\rightarrow$\,2) }}
\newcommand{\Lp}{\mbox{$L^{\prime}_{\rm CO(1-0)}$}}
\newcommand{\LpU}{\mbox{K\,\,km\,\,s$^{-1}$\,\,pc$^2$}}
\newcommand{\eg}{{\sl e.g.,~}}
\newcommand{\ie}{{\sl i.e.,~}}
\newcommand{\pmOne}{\mbox{$^{-1}$}}
\newcommand\tna{\,\tablenotemark{a}}
\newcommand\tnb{\,\tablenotemark{b}}
\newcommand\tnc{\,\tablenotemark{c}}
\newcommand\tnd{\,\tablenotemark{d}}
\newcommand\tne{\,\tablenotemark{e}}
\newcommand\tnf{\,\tablenotemark{f}}
\newcommand\tng{\,\tablenotemark{g}}

@@

\begin{abstract}
We report the detection of \CO line emission in the strongly-lensed submillimeter galaxy\,(SMG) SMM\,J0939+8315 at $z$\,=\,2.2212\,$\pm$\,0.0001, using  
the Combined Array for Research in Millimeter-wave Astronomy (CARMA). 
The SMG is lensed by the radio galaxy 3C220.3 and its companion galaxy at $z$\,=\,0.685. 
This measurement allows us to place constraints on the intrinsic properties
of the cold gas and dust in the interstellar medium (ISM) of the background SMG which hosts a type-2 quasar, as well as on the spectral energy distribution (SED) of the foreground radio galaxy using the marginally resolved continuum 
emission detected at an integrated flux density of $S_\nu$\,=\,9.5\,$\pm$\,0.6 mJy
 at 104 GHz.
We measure a velocity-integrated \CO line intensity of $I_{\rm CO(3-2)}$\,=\,(10.7\,$\pm$\,1.3)\,Jy\,km\,s\pmOne,
corresponding to a lensing- and excitation-corrected CO line luminosity of \Lp\,=\,(2.9\,$\pm$\,0.6)\,$\times$\,10$^{10}$\,(10.1/$\mu_{\rm L}$)\,\LpU, where $\mu_{\rm L}$ is the lensing magnification factor inferred from our lens modeling of the 1\,mm continuum emission. 
 This
translates to a molecular gas mass of $M_{\rm gas}$\,=\,(2.3\,$\pm$\,0.5)\,$\times$\,10$^{10}$\,\Msun. We 
fit optically thick and optically thin modified blackbody models to the SED of the SMG. The preferred optically thick model yields a characteristic dust temperature of $T_{\rm dust}$\,=\,63.1$^{+1.1}_{-1.3}$\,K in the rest-frame, a dust mass of $M_{\rm dust}$\,=\,(5.2\,$\pm$\,2.1)\,$\times$\,10$^8$\,\Msun, and a total infrared (IR) luminosity of $L_{\rm IR}$\,=\,(9.1\,$\pm$\,1.2)\,$\times$10$^{12}$\,\Lsun, after correcting for lensing magnification. We conclude that the intrinsics properties (\eg gas mass, gas mass 
fraction, star formation rate) of the molecular gas reservoir in SMM
J0939+8315 based on our \CO observations is similar to other high redshift
SMGs. 
\end{abstract}
\keywords{galaxies: formation --- galaxies: high-redshift --- submillimeter: galaxies}

\section{Introduction}\label{sec:intro}
Submillimeter-selected galaxies (SMGs) are predominantly found at redshifts $z$\,$\sim$\,1$-$3, during the epoch of stellar mass and 
galaxy assembly, with a tail out to $z>$ 6 \citep{Riechers13a}. 
These galaxies are luminous at submillimeter (submm) wavelengths due to the re-radiation of dust emission peaking at 
rest-frame far-infrared (FIR) wavelengths \citep{blain02a}. 
In the past $\sim$5\,\,years, considerable amounts of effort have been invested into follow-up observations of SMGs that were 
discovered in large sky surveys \citep[\eg H-ATLAS, HerMES; ][]{Eales10a,Oliver12a}, conducted using (sub)-mm facilities. These detailed studies have led to growing consensus that SMGs are a population of high-redshift galaxies that are extremely dusty, gas-rich, 
  and luminous ($\gtrsim$ 10$^{12}$ \Lsun) at the infrared wavebands, with high star formation rates \citep[$\gtrsim $ 500 \Msun yr\pmOne; \eg][]{Lagache05a}.

  To characterize the physical properties of the gas reservoirs in the ISM where active star formation takes place, carbon monoxide (CO) rotational lines have been commonly used as tracers due to its high abundance in the ISM as well as its low excitation energy; the ground state transition line thereby directly probes the cool gas that is essential to fuel star formation \citep[See \eg][]{Carilli13a}. Recent observations of CO in SMGs at $z$\,$\sim$\,1$-$3 have demonstrated that these galaxies have large gas reservoirs typical of \textgreater 10$^{10}$\Msun \citep[\eg][]{Riechers11c,Riechers11d,Ivison11a,Bothwell13a}.

Many recent follow-up observations and thus detailed studies are carried out on SMGs that are gravitationally lensed,
 as lensing amplifies the intrinsic luminosities of these sources, making them the brightest unveiled in large sky surveys \citep{Negrello10a,Vieira10a,Oliver12a}. 
A particularly interesting, peculiar submm-bright lensing system discovered serendipitously  
consists of a type-2 quasar host SMG -- SMM\,J0939+8315 (hereafter SMM\,J0939), lensed by the double-lobed Fanaroff-Riley 
Class II \citep*[FR-II; ][]{Fanaroff74} radio galaxy 3C220.3 and its
companion galaxy B at $z$\,=\,0.685, where the two lensing galaxies are separated by 1\farcs5. 
SMM\,J0939 is currently one of the brightest known lensed
SMGs, with a lensing-magnified flux density of $S_{\rm 250\mu m}$\,=\,440\,$\pm$\,15 mJy. 
Previous detections of CIV\,1459\AA\
 and HeII\,1640\AA\ line emission toward SMM\,J0939 
 place the redshift of this galaxy at $z$\,=\,2.221, and suggest the presence of a type-2 quasar,  
indicating active galactic nucleus activity in this SMG \citep[hereafter H14]{Haas14}.

@@

We adopt a standard $\Lambda$CDM cosmological model throughout this paper, with H$_0$= 69.32 km\,\,Mpc\pmOne\,\,s\pmOne, $\Omega_{\rm M}$\,=\,0.286, $\Omega_\Lambda$=0.713, based on WMAP9 results \citep{Hinshaw13a}.
The luminosity distances at $z$\,=\,0.685 and $z$\,=\,2.221 are 4214 Mpc and 19052 Mpc, respectively; 1$\arcsec$
corresponds to 8.406 kpc at $z$\,=\,2.221, and 7.169 kpc at $z$\,=\,0.685.

\section{Observations}\label{sec:obs}
\subsection{CARMA} \label{sec:carmadata}
Observations of the \CO rotational transition ($\nu_{\rm rest}$\,=\,345.7959899 GHz) toward the background galaxy SMM
J0939 ($z$\,=\,2.221) were carried out using CARMA at a redshifted frequency of $\nu_{obs}$\,=\,107.357\,\,GHz (2.79\,\,mm)  (program ID: cf0142; P.I.: Riechers). The 3\,mm receivers were used to cover the redshifted \CO line and the nearby 2.88\,mm continuum emission, employing a correlator setup providing a bandwidth of 3.75 GHz in each sideband and a spectral resolution of 5.208 MHz ($\sim$14.5 km\,\,s\pmOne). The line was placed in the
upper sideband, with the local oscillator tuned to $\nu_{\rm LO}$\,$\sim$104.2609 GHz.
Observations were carried out under good
weather conditions in the E array configuration on 2014 July 12. This resulted in 1.56 hours of 15 antenna-equivalent on-source time after discarding unusable visibility data.
The nearby source J1039+811 (0.65\,\,Jy) was observed every 20 minutes for
pointing, amplitude, and phase calibration. Mars was observed as the primary
absolute flux calibrator, and the quasar 3C273 was observed as the secondary
flux calibrator. J0927+390 was observed for bandpass calibration, yielding $\sim
$15\% calibration accuracy.
The {\sc MIRIAD} package was used to calibrate and analyze the visibility data, which are deconvolved and imaged using
the CLEAN algorithm with ``natural" weighting. This yields a synthesized clean beam size of 11$\farcs$3\,$\times$\,6\farcs1, at a position angle of $-$56.1$\degr$ east of north for the upper sideband image cube. 
The rms noise of the data prior to continuum subtraction is $\sigma_{\rm ch}$\,=\,8.75\,\,mJy\,\,beam\pmOne\ per bin 
with a channel width of $\sim$29 km\,\,s\pmOne
% spectra
, whereas the final rms noise of the continuum subtracted data is $\sigma_{\rm ch}$\,=\,8.71\,\,mJy\,\,beam\pmOne\ per bin with 
the same channel width, and $\sigma$\,=\,1.00\,Jy\,\,km\,\,s\pmOne\,\,$\rm beam^{-1}$ over a channel 
width of 198 MHz (corresponding to $\sim$553\,\,km\,\,s\pmOne). 
%mom0
The continuum image is created by
averaging over all line-free channels, this yields a synthesized clean beam size of 11\farcs9\,$\times$\,6\farcs5, at a position angle of $-$55.9$\degr$ east of north and an 
rms noise of 0.49\,\,mJy\,\,beam\pmOne.

\section{Results}\label{sec:res}
%\subsection{New Results: Continuum Emission} 
\subsection{New Results: 3C220.3} 
Averaging over all line-free channels, we detect continuum emission at 9$\sigma$ significance at an averaged frequency of $\nu_{cont}$\,=\,104.2106 GHz ($\sim$2.9 mm) in the observed-frame, corresponding to 175.6 GHz ($\sim$1.7 mm) at $z$\,=\,0.685. In this lens system, the 
foreground galaxy (3C220.3) is radio-loud, we thus expect the continuum emission to be dominated by the foreground galaxy (see \S \ref{sec:SEDFg} for details). We use CASA's {\sc imfit} task to estimate the peak position of the continuum emission. The deconvolved source size is (10\farcs2\,$\pm$\,1\farcs4)\,$\times$\,(6\farcs1\,$\pm$\,0\farcs7), and the integrated flux density is 9.46\,$\pm$\,0.64\,\,mJy. At the peak position of the continuum emission, the peak flux density is S$_\nu$\,=\,5.18\,$\pm$\,0.24\,\,mJy\,\,beam\pmOne. An overlay image of the 104 GHz continuum emission on the 9 GHz continuum measurement (H14) is shown in Figure \ref{fig:cont}. This demonstrates that at the resolution of our observations, the continuum emission is marginally resolved. It is therefore plausible that non-thermal emission from both the lobes and the radio core dominate the integrated flux density in our measurement.

The frequency range of our observations covers the HCO$^+$(2$-$1), HNC($J$\,=\,2\,$\rightarrow$\,1), and H$_2$O(3$_{13}$\,$-$\,2$_{20}$) 
transition line emission in the foreground galaxy, at 
the redshifted frequencies of 105.86, 107.71, and 108.79\,\,GHz, respectively. We establish 3$\sigma$ upper limits employing a typical line width of 
$\sim$\,300\,\,km\,\,s\pmOne, based on the CO($J$\,=\,1\,$\rightarrow$\,0) line measurements in the sample of local radio galaxies \citep[$z$ $<$ 0.1; ][]{Smolcic11a}, resulting in 3$\sigma$ of 7.84\,\,Jy\,\,km\,\,s\pmOne.\\ \\
Question for DR: 3sigma using FWHM or total line width (FWZI?)

\begin{figure*}[tbph]
\centering
\includegraphics[width=0.80\textwidth]{Figure/ContPanel.pdf}
\caption{Left: Contour map of the 104 GHz continuum emission in 3C220.3. The beam size is 11\farcs9\,$\times$\,6\farcs5, at P.A.\,=\,
$-$56$\degr$, as indicated in the bottom left corner. Right: Contours of the CARMA 104 GHz continuum emission (red) from the 
foreground radio galaxy 3C220.3 overlaid on the 9 GHz emission (green contours and grayscale; H14). The synthesized beam size of the VLA observations is 0$\farcs$6\,$\times$\,0$\farcs$2, at P.A. 
76$\degr$. The central cross on each image indicates the position of the radio core of 3C220.3. The contour levels of the 104 GHz continuum emission start at $\pm$3$\sigma$, incrementing at steps 
of $\pm$1$\sigma$ of 0.5 mJy beam\pmOne; the contour levels of the 9 GHz continuum 
emission start at $\pm$4$\sigma$ where $\sigma$\,=\,0.064 mJy beam\pmOne\ and increment at steps of $\pm$2$^n\sigma$, 
where $n$ is a positive integer.
\label{fig:cont}}
\end{figure*}
%\subsection{New Results: \CO Line Emission}
\subsection{New Results: SMM\,J0939\\ \CO Line Emission}
We detect \CO line emission at $\sim$10(?yes?no?)$\sigma$ significance toward the background SMG SMM\,J0939 at $z$\,=\,2.221.
The spatial extent of this SMG is $\sim$5$\arcsec$, as shown in the Submillimeter Array (SMA) 1\,mm dust continuum in Figure \ref{fig:mom0}; as such, the detected \CO line emission is spatially unresolved. 
The line profile in Figure \ref{fig:mom0} is therefore extracted at the peak position of the unresolved CO emission. Fitting a four-parameter single Gaussian to the spectrum yields a peak flux density of 21.83\,$\pm$\,2.68\,\,mJy, superimposed on a continuum level of 4.19\,$\pm$\,0.49\,\,mJy, and full width at half-maximum (FWHM) of 557\,$\pm$\,36\,\,km\,\,s\pmOne. 
We construct a velocity-integrated (0th moment) map of the \CO line 
emission from the data after subtracting continuum emission in the visibility plane. This results in a velocity-integrated \CO line flux of $S_{\rm CO}$\,=\,10.7\,$\pm$\,1.3 Jy km\,\,s\pmOne\ over the FWZI velocity range of $\Delta v\sim$\,914 km\,\,s\pmOne, the uncertainty does not include $\sim$\,15\% calibration uncertainty. We ignore primary beam correction given that the source is close to the phase center and is unresolved (\ie much smaller than the primary beam size). Our \CO line measurement confirms the redshift of SMM\,J0939, yielding $z$\,=\,2.22122\,$\pm$\,0.00007.

\begin{figure*}[tbph] 
\centering
\includegraphics[width=0.8\textwidth]{Figure/LinePanel.pdf}
\includegraphics[width=0.65\textwidth]{Figure/smmj0939-co32_spec.eps}
\caption{Top Left: Continuum-subtracted moment-0 map of \CO line emission toward 
the background SMG with $\sigma$\,=\,1.00\,Jy\,\,km\,\,s\pmOne\ beam\pmOne\ over a velocity range of $\Delta v\sim$553\,km\,\,s\pmOne. The angular resolution is 11$\farcs$3\,$\times$\,6\farcs1, at P.A.\,=\,$-$56\degr, as indicated in the bottom left corner. 
Top Right: Contours of the \CO line emission (red) overlaid on the SMA 1\,mm dust continuum (green contours and grayscale; H14) with $\sigma_{\rm 1\,mm}$\,=\,0.84 mJy beam\pmOne. The beam size of the SMA data is 1\farcs4$ \times $1\farcs2, P.A. $-$34\degr, as shown 
in the bottom left corner. 
The central cross on each image corresponds to the same coordinates as in Figure \ref{fig:cont}. The contour levels start at $\pm$3$\sigma$, incrementing at
steps of $\pm$1$\sigma$. 
Bottom: 
Spectrum extracted at the peak position of CO line emission, with a spectral resolution of $\Delta v$ $\sim$29 km\,\,s\pmOne\, and an rms of $\sigma_{\rm ch}$\,=\,8.75 mJy beam\pmOne\ per channel.
Solid black line shows the Gaussian fit to the \CO line profile. Yellow histogram shows the 
flux density as a function of velocity offset, where the velocity scale is relative to $z$\,=\,2.221. 
%where 0 km\,\,s\pmOne\ corresponds to $z$\,=\,2.221. 
\label{fig:mom0}}
\end{figure*}

@@

We perform SED fitting to the IR photometric data of SMM\,J0939 using {\sc mbb\_emcee} (see \S \ref{sec:SEDBg}), this code uses MCMC to fully sample the parameter space of each parameter. The bolometric IR luminosity and dust mass are then derived from the set of parameter values that maximize the likelihood. Figure \ref{fig:sedlikelihood} shows the correlations between each pair of parameters (off-diagonal) as well as the marginalized posterior probability distribution of each parameter (diagonal) for both optically thick and optically thin models. The set of best-fit parameters are denoted as black crosses in the 2D correlation plots, and vertical lines in the marginalized posterior probability distribution plots.

>>>>

%\documentclass{emulateapj}
\documentclass[twocolumn,apj,numberedappendix]{emulateapj}
\usepackage{hyperref}
\newcommand{\vdag}{(v)^\dagger}
\newcommand{\myemail}{tleung@astro.cornell.edu}
\newcommand{\Msun}{\mbox{$M_{\odot}$}}
\newcommand{\Rsun}{\mbox{R$_{\odot}$}}
\newcommand{\Lsun}{\mbox{L$_{\odot}$}}
\newcommand{\rarr}{$\rightarrow$}
\newcommand{\CO}{\mbox{CO($J$\,=\,3\,$\rightarrow$\,2) }}
\newcommand{\Lp}{\mbox{$L^{\prime}_\textrm{CO(1-0)}$}}
\newcommand{\LpU}{\mbox{K\,\,km\,\,s$^{-1}$\,\,pc$^2$}}
%\newcommand{\eg}{{\sl e.g.,}}
\newcommand{\eg}{{\sl e.g.,~}}
\newcommand{\ie}{{\sl i.e.,~}}
\newcommand{\pmOne}{\mbox{$^{-1}$}}
\newcommand\tna{\,\tablenotemark{a}}
\newcommand\tnb{\,\tablenotemark{b}}
\newcommand\tnc{\,\tablenotemark{c}}
\newcommand\tnd{\,\tablenotemark{d}}
\newcommand\tne{\,\tablenotemark{e}}
\newcommand\tnf{\,\tablenotemark{f}}
\newcommand\tng{\,\tablenotemark{g}}

@@

\begin{abstract}
We report the detection of \CO line emission in the strongly-lensed submillimeter galaxy\,(SMG) SMM\,J0939+8315 at $z$\,=\,2.2212\,$\pm$\,0.001, using  
the Combined Array for Research in Millimeter-wave Astronomy (CARMA). 
The SMG is lensed by the radio galaxy 3C220.3 and its companion galaxy at $z$\,=\,0.685. 
This measurement allows us to place constraints on the intrinsic properties
of the cold gas and dust in the interstellar medium (ISM) of the background SMG which hosts a type-2 quasar, as well as on the spectral energy distribution (SED) of the foreground radio galaxy using the marginally resolved continuum 
emission detected at an integrated flux density of $S_\nu$\,=\,9.5\,$\pm$\,0.6 mJy
 at 104 GHz.
We measure a velocity-integrated \CO line intensity of $I_\textrm{CO(3-2)}$\,=\,(10.7\,$\pm$\,1.3)\,Jy\,km\,s\pmOne,
corresponding to a lensing- and excitation-corrected CO line luminosity of \Lp\,=\,(2.9\,$\pm$\,0.6)\,$\times$\,10$^{10}$\,(10.1/$\mu_\textrm{L}$)\,\LpU, where $\mu_\textrm{L}$ is the lensing magnification factor inferred from our lens modeling of the 1\,mm continuum emission. 
 This
translates to a molecular gas mass of $M_\textrm{gas}$\,=\,(2.3\,$\pm$\,0.5)\,$\times$\,10$^{10}$\,\Msun. We 
fit optically thick and optically thin modified blackbody models to the SED of the SMG. The preferred optically thick model yields a characteristic dust temperature of $T_\textrm{dust}$\,=\,63.1$^{+1.1}_{-1.3}$\,K in the rest-frame, a dust mass of $M_\textrm{dust}$\,=\,(5.2\,$\pm$\,2.1)\,$\times$\,10$^8$\,\Msun, and a total infrared (IR) luminosity of $L_\textrm{IR}$\,=\,(9.1\,$\pm$\,1.2)\,$\times$10$^{12}$\,\Lsun, after correcting for lensing magnification. We conclude that the intrinsics properties (\eg gas mass, gas mass 
fraction, star formation rate) of the molecular gas reservoir in SMM
J0939+8315 based on our \CO observations is similar to other high redshift
SMGs. \\
***Will revise after completing the discussion section.***
\end{abstract}
\keywords{galaxies: formation --- galaxies: high-redshift --- submillimeter: galaxies}

\section{Introduction}\label{sec:intro}
Submillimeter-selected galaxies (SMGs) are predominantly found at redshifts $z$\,$\sim$\,1\,--\,3, during the epoch of stellar mass and 
galaxy assembly, with a tail out to $z>$ 6 \citep{Riechers13a}. 
These galaxies are luminous at submillimeter (submm) wavelengths due to the re-radiation of dust emission peaking at 
rest-frame far-infrared (FIR) wavelengths \citep{blain02a}. 
In the past $\sim$5~years, considerable amounts of effort have been invested into follow-up observations of SMGs that were 
discovered in large sky surveys \citep[\eg H-ATLAS, HerMES; ][]{Eales10a,Oliver12a}, conducted using (sub)-mm facilities. These detailed studies have led to growing consensus that SMGs are a population of high-redshift galaxies that are extremely dusty, gas-rich, 
  and luminous ($\gtrsim$ 10$^{12}$ \Lsun) at the infrared wavebands, with high star formation rates \citep[$\gtrsim $ 500 \Msun yr\pmOne; \eg][]{Lagache05a}.

  To characterize the physical properties of the gas reservoirs in the ISM where active star formation takes place, carbon monoxide (CO) rotational lines have been commonly used as tracers due to its high abundance in the ISM as well as its low excitation energy; the ground state transition line thereby directly probes the cool gas that is essential to fuel star formation \citep[See \eg][]{Carilli13a}. Recent observations of CO in SMGs at $z$\,$\sim$\,1\,--\,3 have demonstrated that these galaxies have large gas reservoirs typical of \textgreater 10$^{10}$\Msun \citep[\eg][]{Riechers11c,Riechers11d,Ivison11a,Bothwell13a}.

Many recent follow-up observations and thus detailed studies are carried out on SMGs that are gravitationally lensed,
 as lensing amplifies the intrinsic luminosities of these sources, making them the brightest unveiled in large sky surveys \citep{Negrello10a,Vieira10a,Oliver12a}. 
A particularly interesting, peculiar submm-bright lensing system discovered serendipitously  
consists of a type-2 quasar host SMG --- SMM\,J0939+8315 (hereafter SMM\,J0939), lensed by the double-lobed Fanaroff-Riley 
Class II \citep*[FR-II; ][]{Fanaroff74} radio galaxy 3C220.3 and its
companion galaxy B at $z$\,=\,0.685, where the two lensing galaxies are separated by 1\farcs5. 
SMM\,J0939 is currently one of the brightest known lensed
SMGs, with a lensing-magnified flux density of $S_\textrm{250\micron m}$\,=\,440\,$\pm$\,15 mJy. 
Previous detections of CIV\,1459\AA\
 and HeII\,1640\AA\ line emission toward SMM\,J0939 
 placed this galaxy at $z$\,=\,2.221, and suggested the presence of a type-2 quasar,  
indicating active galactic nucleus activity in this SMG \citep[hereafter H14]{Haas14}.

@@

We adopt a standard $\Lambda$CDM cosmological model throughout this paper, with H$_0$= 69.32 km\,\,Mpc\pmOne\,\,s\pmOne, $\Omega_\textrm{M}$\,=\,0.286, $\Omega_\Lambda$=0.713, based on WMAP9 results \citep{Hinshaw13a}.
The luminosity distances at $z$\,=\,0.685 and $z$\,=\,2.221 are 4214 Mpc and 19052 Mpc, respectively; 1$\arcsec$
corresponds to 8.406 kpc at $z$\,=\,2.221, and 7.169 kpc at $z$\,=\,0.685.

\section{Observations}\label{sec:obs}
\subsection{CARMA} \label{sec:carmadata}
Observations of the \CO rotational transition ($\nu_\textrm{rest}$\,=\,345.7959899 GHz) toward the background galaxy SMM
J0939 ($z$\,=\,2.221) were carried out using CARMA at a redshifted frequency of $\nu_{obs}$\,=\,107.357\,\,GHz (2.79\,\,mm)  (program ID: cf0142; P.I.: Riechers). The 3\,mm receivers were used to cover the redshifted \CO line and the nearby 2.88\,mm continuum emission, employing a correlator setup providing a bandwidth of 3.75 GHz in each sideband and a spectral resolution of 5.208 MHz ($\sim$14.5 km\,\,s\pmOne). The line was placed in the
upper sideband, with the local oscillator tuned to $\nu_\textrm{LO}$\,$\sim$104.2609 GHz.
Observations were carried out under good
weather conditions in the E array configuration on 2014 July 12. This resulted in 1.56 hours of 15 antenna-equivalent on-source time after discarding unusable visibility data.
The nearby source J1039+811 (0.65\,\,Jy) was observed every 20 minutes for
pointing, amplitude, and phase calibration. Mars was observed as the primary
absolute flux calibrator, and the quasar 3C273 was observed as the secondary
flux calibrator. J0927+390 was observed for bandpass calibration, yielding $\sim
$15\% calibration accuracy.
The {\sc MIRIAD} package was used to calibrate and analyze the visibility data, which are deconvolved and imaged using
the CLEAN algorithm with ``natural" weighting. This yields a synthesized clean beam size of 11$\farcs$3\,$\times$\,6\farcs1, at a position angle of $-$56.1$\degr$ east of north for the upper sideband image cube. 
The rms noise of the data prior to continuum subtraction is $\sigma_\textrm{ch}$\,=\,8.75\,\,mJy\,\,beam\pmOne\ per bin 
with a channel width of $\sim$29 km\,\,s\pmOne
% spectra
, whereas the final rms noise of the continuum subtracted data is $\sigma_\textrm{ch}$\,=\,8.71\,\,mJy\,\,beam\pmOne\ per bin with 
the same channel width, and $\sigma$\,=\,1.00\,Jy\,\,km\,\,s\pmOne\,\,$\rm beam^{-1}$ over a channel 
width of 198 MHz (corresponding to $\sim$553\,\,km\,\,s\pmOne). 
%mom0
The continuum image is created by
averaging over all line-free channels, this yields a synthesized clean beam size of 11\farcs9\,$\times$\,6\farcs5, at a position angle of $-$55.9$\degr$ east of north and an 
rms noise of 0.49\,\,mJy\,\,beam\pmOne.

\section{Results}\label{sec:res}
%\subsection{New Results: Continuum Emission} 
\subsection{New Results: 3C220.3} 
Averaging over all line-free channels, we detect continuum emission at 9$\sigma$ significance at an averaged frequency of $\nu_{cont}$\,=\,104.2106 GHz ($\sim$2.9 mm) in the observed-frame, corresponding to 175.6 GHz ($\sim$1.7 mm) at $z$\,=\,0.685. In this lens system, the 
foreground galaxy (3C220.3) is radio-loud, we thus expect the continuum emission to be dominated by the foreground galaxy (see \S \ref{sec:SEDFg} for details). We use CASA's {\sc imfit} task to estimate the peak position of the continuum emission. The deconvolved source size is (10\farcs2\,$\pm$\,1\farcs4)\,$\times$\,(6\farcs1\,$\pm$\,0\farcs7), and the integrated flux density is 9.46\,$\pm$\,0.64\,\,mJy. At the peak position of the continuum emission, the peak flux density is S$_\nu$\,=\,5.18\,$\pm$\,0.24\,\,mJy\,\,beam\pmOne. An overlay image of the 104 GHz continuum emission on the 9 GHz continuum measurement (H14) is shown in Figure~\ref{fig:cont}. This demonstrates that at the resolution of our observations, the continuum emission is marginally resolved. It is therefore plausible that non-thermal emission from both the lobes and the radio core dominate the integrated flux density in our measurement.

The frequency range of our observations covers the HCO$^+$(2\,\rarr\,1), HNC($J$\,=\,2\,$\rightarrow$\,1), and H$_2$O(3$_{13}$\,\rarr\,2$_{20}$) 
transition line emission in the foreground galaxy, at 
the redshifted frequencies of 105.86, 107.71, and 108.79\,\,GHz, respectively. We establish 3$\sigma$ upper limits employing a typical FWHM line width of 
$\sim$\,300\,\,km\,\,s\pmOne, based on the CO($J$\,=\,1\,$\rightarrow$\,0) line measurements in a sample of local radio galaxies \citep[$z$ $<$ 0.1; ][]{Smolcic11a}, resulting in 3$\sigma$ of 2.44\,\,Jy\,\,km\,\,s\pmOne.

\begin{figure*}[tbph]
\centering
\includegraphics[width=0.80\textwidth]{Figure/ContPanel.pdf}
\caption{Left: Contour map of the 104 GHz continuum emission in 3C220.3. The beam size is 11\farcs9\,$\times$\,6\farcs5, at P.A.\,=\,
$-$56$\degr$, as indicated in the bottom left corner. Right: Contours of the CARMA 104 GHz continuum emission (red) from the 
foreground radio galaxy 3C220.3 overlaid on the 9 GHz emission (green contours and grayscale; H14). The synthesized beam size of the VLA observations is 0$\farcs$6\,$\times$\,0$\farcs$2, at P.A. 
76$\degr$. The central cross on each image indicates the position of the radio core of 3C220.3. The contour levels of the 104 GHz continuum emission start at $\pm$3$\sigma$, incrementing at steps 
of $\pm$1$\sigma$ of 0.5 mJy beam\pmOne; the contour levels of the 9 GHz continuum 
emission start at $\pm$4$\sigma$ where $\sigma$\,=\,0.064 mJy beam\pmOne\ and increment at steps of $\pm$2$^n\sigma$, 
where $n$ is a positive integer.
\label{fig:cont}}
\end{figure*}
%\subsection{New Results: \CO Line Emission}
\subsection{New Results: SMM\,J0939\\ \CO Line Emission}
We detect \CO line emission at $\sim$8$\sigma$ significance toward the background SMG SMM\,J0939 at $z$\,=\,2.221.
The spatial extent of this SMG is $\sim$5$\arcsec$, as shown in the Submillimeter Array (SMA) 1\,mm dust continuum in Figure~\ref{fig:mom0}; as such, the detected \CO line emission is spatially unresolved. 
The line profile in Figure~\ref{fig:mom0} is therefore extracted at the peak position of the unresolved CO emission. Fitting a four-parameter single Gaussian to the spectrum yields a peak flux density of 21.83\,$\pm$\,2.68\,\,mJy, superimposed on a continuum level of 4.19\,$\pm$\,0.49\,\,mJy, and a full width at half-maximum (FWHM) line width of 557\,$\pm$\,36\,\,km\,\,s\pmOne. 
We construct a velocity-integrated (0th moment) map of the \CO line 
emission from the data after subtracting continuum emission in the visibility plane. This results in a velocity-integrated \CO line flux of $S_\textrm{CO}$\,=\,10.7\,$\pm$\,1.3 Jy km\,\,s\pmOne\ over the FWZI velocity range of $\Delta v\sim$\,914 km\,\,s\pmOne, the uncertainty does not include $\sim$\,15\% calibration uncertainty. We ignore primary beam correction given that the source is close to the phase center and is unresolved (\ie much smaller than the primary beam size). Our \CO line measurement confirms the redshift of SMM\,J0939, yielding $z$\,=\,2.2212\,$\pm$\,0.0010.

\begin{figure*}[tbph] 
\centering
\includegraphics[width=0.8\textwidth]{Figure/LinePanel.pdf}
\includegraphics[width=0.65\textwidth]{Figure/smmj0939-co32_spec.eps}
\caption{Top Left: Continuum-subtracted moment-0 map of \CO line emission toward 
the background SMG with $\sigma$\,=\,1.00\,Jy\,\,km\,\,s\pmOne\ beam\pmOne\ over a velocity range of $\Delta v\sim$553\,km\,\,s\pmOne. The angular resolution is 11$\farcs$3\,$\times$\,6\farcs1, at P.A.\,=\,$-$56\degr, as indicated in the bottom left corner. 
Top Right: Contours of the \CO line emission (red) overlaid on the SMA 1\,mm dust continuum (green contours and grayscale; H14) with $\sigma_\textrm{1\,mm}$\,=\,0.84 mJy beam\pmOne. The beam size of the SMA data is 1\farcs4$ \times $1\farcs2, P.A. $-$34\degr, as shown 
in the bottom left corner. 
The central cross on each image corresponds to the same coordinates as in Figure~\ref{fig:cont}. The contour levels start at $\pm$3$\sigma$, incrementing at
steps of $\pm$1$\sigma$. 
Bottom: 
Spectrum extracted at the peak position of CO line emission, with a spectral resolution of $\Delta v$ $\sim$29 km\,\,s\pmOne\, and an rms of $\sigma_\textrm{ch}$\,=\,8.75 mJy beam\pmOne\ per channel.
Solid black line shows the Gaussian fit to the \CO line profile. Yellow histogram shows the 
flux density as a function of velocity offset, where the velocity scale is relative to $z$\,=\,2.221. 
%where 0 km\,\,s\pmOne\ corresponds to $z$\,=\,2.221. 
\label{fig:mom0}}
\end{figure*}

@@

We perform SED fitting to the IR photometric data of SMM\,J0939 using {\sc mbb\_emcee} (see \S \ref{sec:SEDBg}), this code uses MCMC to fully sample the parameter space of each parameter. The bolometric IR luminosity and dust mass are then derived from the set of parameter values that maximize the likelihood. Figure~\ref{fig:sedlikelihood} shows the correlations between each pair of parameters (off-diagonal) as well as the marginalized posterior probability distribution of each parameter (diagonal) for both optically thick and optically thin models. The set of best-fit parameters are denoted as black crosses in the 2D correlation plots, and vertical lines in the marginalized posterior probability distribution plots. BLAH
